---
title: "Counts of Ugandan registered voters for the 2016 General Election"
author: "Daniel Emaasit"
date: "February 11, 2016"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# UGvoters16

## What is this?
**UGvoters** is a package for the counts of Ugandan registered voters for the 2016 presidential election provided by the [Electoral Commision](http://www.ec.or.ug/) (EC) of Uganda. This package contains the number of registered voters by polling station. This "controversial" data was claimed to contain atleast 20,000 "ghost voters" by members of the Ugandan media because the total count from the each polling station are not equal to the totals reported by the Electoral Commission.

## How to use it
Before you can use the data in R, you need to download it from Github using the following commands:
```{r install_package, eval = FALSE, warning = FALSE}
installed.packages("devtools")
devtools::install_github("emaasit/UGvoters16")
library(UGvoters16)
```

After loading the library, you can load the data using the following command:
```{r load_data, eval = FALSE, warning = FALSE}
data(UGvoters16)
```

## What can you do with it?
You can explore for yourself and see why the Ugandan media claimed it has atleast 20,000 "ghost voters".
